### 2014-02-20 paper/retrofit.tex
minor

\begin{figure}
\begin{code}
lop  ::=  canFlowTo | lub | glb
iv   ::=  id | il | true | false | unit
ie   ::=  iv | x | y | ie lop ie | getLabel | setLabel ie
       |  fork ie | send ie ie ie | x, y <= recv. ie ie |  IT te
iE   ::=  iE lop ie | iv lop iE | setLabel iE | fork iE 
       |  send iE ie ie | send iv iE ie | send iv iv iE
       |  x, y <= recv. ie ie |  IT tE

@@

\begin{mathpar}
\inferrule[I-getLabel]
{ }
{|
iconf iS (lconf id il tS (iniE (getLabel)), ldots)
-->
iconf iS (lconf id il tS (iniE il), ldots)
|}
\and
\inferrule[I-setLabel]
{ |il canFlowTo il'| }
{|
iconf iS (lconf id il tS (iniE (setLabel il')), ldots)
-->
iconf iS (lconf id il' tS (iniE unit), ldots)
|}
\and
\inferrule[I-fork]
{ 
|iS' = iS [ id' mapsto nil ]|
}
{|
iconf iS (lconf id il tS (iniE (fork (IT te))), ldots)
-->
iconf iS' (lconf id il tS (iniE id'), ldots, lconf id' il tS te)
|}
{|fresh (id')|}
\and
\inferrule[I-send]
{
|il canFlowTo il'|\\
|iS(id') = Q|\\
|iS' = iS [ id' mapsto (il', id,  ie) cons Q ]|
}
{|
iconf iS (lconf id il tS (iniE (send id' il' ie))), ldots)
-->
iconf iS' (lconf id il tS (iniE unit), ldots)
|}
\and
\inferrule[I-recv]
{
| filter il (iS(id)) = (il', id', ie') :: Q'|\\
| iS' = iS[id mapsto Q']|
}
{|
iconf iS (lconf id il tS (iniE (x, y <= recv. ie1 ie2))), ldots)
-->
iconf iS' (lconf id il tS (iniE ({ie'/x,id'/y} ie1)), ldots)
|}
\and
\inferrule[I-noRecv]
{
| filter il (iS(id)) = nil|\\
| iS' = iS[id mapsto nil]|
}
{|
iconf iS (lconf id il tS (iniE (x, y <= recv. ie1 ie2))), ldots)
-->
iconf iS' (lconf id il tS (iniE ie2), ldots)
|}
\and
\inferrule[I-border]
{ }
{| iniE (IT (TI (ie))) --> iniE ie |}
\and
\inferrule[T-border]
{ }
{| intE (TI (IT (te))) --> intE te |}
\end{mathpar}

>>>>

\begin{figure}
\begin{code}
lop  ::=  canFlowTo | lub | glb
iv   ::=  id | il | true | false | unit
ie   ::=  iv | x | y | ie lop ie | getLabel | setLabel ie
       |  fork ie | send ie ie ie | x, y <= recv. ie ie |  IT te
iE   ::=  iE lop ie | iv lop iE | setLabel iE | fork iE 
       |  send iE ie ie | send iv iE ie | send iv iv iE
       |  x, y <= recv. ie ie |  IT tE
Q    ::=  nil | (il, id, ie) :: Q

@@

\begin{mathpar}
\inferrule[I-getLabel]
{ }
{|
iconf iS (lconf id il tS (iniE (getLabel)), ldots)
-->
iconf iS (lconf id il tS (iniE il), ldots)
|}
\and
\inferrule[I-setLabel]
{ |il canFlowTo il'| }
{|
iconf iS (lconf id il tS (iniE (setLabel il')), ldots)
-->
iconf iS (lconf id il' tS (iniE unit), ldots)
|}
\and
\inferrule[I-fork]
{ 
|iS' = iS [ id' mapsto nil ]|
}
{|
iconf iS (lconf id il tS (iniE (fork (IT te))), ldots)
-->
iconf iS' (lconf id il tS (iniE id'), ldots, lconf id' il tS te)
|}
{|fresh (id')|}
\and
\inferrule[I-send]
{
|il canFlowTo il'|\\
|iS(id') = Q|\\
|iS' = iS [ id' mapsto (il', id,  ie) :: Q ]|
}
{|
iconf iS (lconf id il tS (iniE (send id' il' ie))), ldots)
-->
iconf iS' (lconf id il tS (iniE unit), ldots)
|}
\and
\inferrule[I-recv]
{
| filter il (iS(id)) = (il', id', ie') :: Q'|\\
| iS' = iS[id mapsto Q']|
}
{|
iconf iS (lconf id il tS (iniE (x, y <= recv. ie1 ie2))), ldots)
-->
iconf iS' (lconf id il tS (iniE ({ie'/x,id'/y} ie1)), ldots)
|}
\and
\inferrule[I-noRecv]
{
| filter il (iS(id)) = nil|\\
| iS' = iS[id mapsto nil]|
}
{|
iconf iS (lconf id il tS (iniE (x, y <= recv. ie1 ie2))), ldots)
-->
iconf iS' (lconf id il tS (iniE ie2), ldots)
|}
\and
\inferrule[I-border]
{ }
{| iniE (IT (TI (ie))) --> iniE ie |}
\and
\inferrule[T-border]
{ }
{| intE (TI (IT (te))) --> intE te |}
\end{mathpar}
